Picky with peakpicking: assessing chromatographic peak quality with simple

### 2023-07-21 manuscript/manuscript.Rmd
Adding Bai2022 reference

This model outperforms the previously reported logistic regression model in @Kantz2019 and is highly simplified. There, they used a nineteen-parameter multiple logistic regression model and found a maximum performance of 80% GFF and an FDR of 34% on a cross-validated second cohort, similar to our cross-dataset testing. Our final two-parameter model also had an 80% GFF at a 0.5 likelihood threshold, but a significantly lower FDR of ~22.9%. This increased performance is likely due to our use of the metrics recalculated from the raw data, as their metrics were only calculated from the default MzMine2 peak parameters reported: similar to our XCMS-only model.

>>>>

This model outperforms the previously reported logistic regression model in @Kantz2019 and is highly simplified. There, they used a nineteen-parameter multiple logistic regression model and found a maximum performance of 80% GFF and an FDR of 34% on a cross-validated second cohort, similar to our cross-dataset testing. Our final two-parameter model also had an 80% GFF at a 0.5 likelihood threshold, but a significantly lower FDR of ~22.9%. This increased performance is likely due to our use of the metrics recalculated from the raw data, as their metrics were only calculated from the default MzMine2 peak parameters reported: similar to our XCMS-only model. Previous work on a "shape-orientated" algorithm also established the utility of testing the extracted ion chromatogram against a Gaussian shape [@Bai2022]. There, the use of a Marr wavelet had GFF values in the 98-100% range but very high FDR values of 82-91%, representing a very lenient threshold much closer to the XCMS or ADAP defaults.
